### 2022-05-25 examples/templates/index.qmd
Docs (#9)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

    - rawinventor.parquet

@@

```{python}
summarizers = {filename: InventorDisambiguationSummary(filename) for filename in ['rawinventor.parquet'] }
```

@@

```{python}
compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
```

@@

## rawinventor.parquet

```{python}
summarizers["rawinventor.parquet"].get_top_inventors(n=20)
```

@@

```{python}
compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
```

@@

    return df["patent_id"]

disambiguations = {filename: read_disambiguation(filename) for filename in ['rawinventor.parquet'] }
```

@@

### rawinventor.parquet

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_israeli_inventors_benchmark()), by="reference")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["rawinventor.parquet"], load_patentsview_inventors_benchmark()), by="reference")
```

>>>>

    - rawinventor.tsv

- **Disambiguation results:**

    - disambiguation.tsv

@@

```{python}
summarizers = {filename: InventorDisambiguationSummary(filename, processed_data_dir=".") for filename in ['rawinventor.tsv'] }
```

@@

```{python}
compare_plots(*[s.plot_cluster_size_distribution(range=(0.5,10.5)) for s in summarizers.values()])
```

@@

## rawinventor.tsv

```{python}
summarizers["rawinventor.tsv"].get_top_inventors(n=20)
```

@@

```{python}
compare_plots(*[s.plot_cluster_unique_name_distribution(range=(0, 100)) for s in summarizers.values()])
```

@@

    return df[df.columns[0]]

disambiguations = {filename: read_disambiguation(filename) for filename in ['disambiguation.tsv'] }
```

@@

### disambiguation.tsv

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["disambiguation.tsv"], load_israeli_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_split(disambiguations["disambiguation.tsv"], load_patentsview_inventors_benchmark()), by="prediction")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["disambiguation.tsv"], load_israeli_inventors_benchmark()), by="reference")
```

@@

```{python}
#| column: page
style_and_display(inspect_clusters_to_merge(disambiguations["disambiguation.tsv"], load_patentsview_inventors_benchmark()), by="reference")
```

### 2022-05-25 pv_evaluation/templates/inventor/0-report.qmd
Docs (#9)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

- **Disambiguation summary tables:**
{% for filename in summary_table_files %}
    - {{ filename }}
{% endfor %}
- **Disambiguation results:**
{% for filename in disambiguation_files %}
    - {{ filename }}
{% endfor %}

>>>>

- **Disambiguation summary tables:**
{% for filename in summary_table_files %}
    - {{ filename }}
{% endfor %}

### 2022-05-25 pv_evaluation/templates/inventor/2-summary.qmd
Docs (#9)
* update

* add sphinx doc

* update

* add html docs

* add module docs

* update

```{python}
compare_plots(*[s.plot_cluster_size_distribution(range=(0.5,10.5)) for s in summarizers.values()])
```

@@

```{python}
compare_plots(*[s.plot_cluster_unique_name_distribution(range=(0, 100)) for s in summarizers.values()])
```

>>>>

```{python}
compare_plots(*[s.plot_cluster_size_distribution() for s in summarizers.values()])
```

@@

```{python}
compare_plots(*[s.plot_cluster_unique_name_distribution() for s in summarizers.values()])
```
